---
author: "Oliver Summers"
date: 'Date of Analysis: `r Sys.Date()`'
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(scipen = 999)

# required packages
library(bearing)
library(dplyr)
library(sf)
library(ggplot2)
library(summarytools)
library(kableExtra)

# ggplot theme - can make bearing one in the future
theme_set(theme_minimal())

# Define the subject property
# p_id <- standardised_data$pid[1] # get rid of this when using it in a loop

define_subject(standardised_data,
               subject_pid = p_id)
```

---
title: "Market Analysis: `r subject_address`"
---
\newpage

## Initial Leaflet Plot - Dataset A


```{r}
leaflet_plot(standardised_data, 
             subject_lng, 
             subject_lat)
```

This plot shows all of the properties in the dataset. 

\newpage
\blandscape
## Grouped Properties (Clusters) - Dataset B

`r subject_address` is in cluster `r get_subj_cluster(sales_with_knn, subject_pid)` of `r m`.

### Summary stats of cluster

```{r}
subj_cluster <- get_subj_cluster(sales_with_knn, subject_pid)

sales_with_knn <- sales_with_knn %>% 
  mutate(subject_cluster = ifelse(m == subj_cluster, 'yes', 'no'))

sales_with_knn %>% 
  # mutate(across(where(is.numeric), format, digits=4,nsmall = 0)) %>% 
  filter(m == subj_cluster) %>%
  summarytools::descr() %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')


# sales_with_knn %>% 
#   select(-c(knn, longitude,  latitude, m)) %>% 
#   kbl %>% 
#   kable_paper("hover", full_width = F) %>% 
#   kable_styling(latex_options='scale_down')
```
\elandscape

```{r}
facet_boxplot(sales_with_knn, variable = 'sales_price')
```

```{r}
facet_hist(sales_with_knn, 'sales_price')
```

```{r}
sales_time_scatter(sales_with_knn)
```

```{r}
ggplot2::ggplot(sales_with_knn, ggplot2::aes(x = sales_price, fill = subject_cluster)) +
  ggplot2::geom_histogram(data=subset(sales_with_knn,subject_cluster == 'no'), alpha = 0.6) +
  ggplot2::geom_histogram(data=subset(sales_with_knn,subject_cluster == 'yes'), alpha = 0.6) +
  scale_fill_manual(name="Subject Cluster", values=c("darkgreen","lightblue"),labels=c("no","yes"))
```

### Within Cluster Analysis

```{r}
ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = sales_price)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  xlab('Sales Price')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = as.numeric(as.character(year_sold)))) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  xlab('Year Sold')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = gba)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = sales_price, y = no_br, group = no_br)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2) +
  xlab('Sales Price') +
  ylab('Number of Bedrooms')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = gba, y = no_br, group = no_br)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2) +
  xlab('Sq Ft') +
  ylab('Number of bedrooms')

sales_time_scatter(sales_with_knn %>% 
                     filter(m == subj_cluster))

sales_time_scatter(sales_with_knn %>% 
                     filter(m == subj_cluster),
                   sales_var = 'ppsf')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = gba, y = sales_price)) +
  geom_point() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2) +
  geom_smooth(method='lm', formula= y~x)
```


### Plot same cluster apartments

This plot shows `r subject_address` and the properties that were found to be in the same cluster as it.
```{r}
plot_clusters(sales_with_knn)
```

\newpage
\blandscape

## Nearest Neighbours - Dataset C

This dataset includes `r subject_address` and it's `r k` nearest neighbours from the knn algorithm.

### NN summary stats


```{r}
sales_nn <- get_nn(sales_with_knn, subject_pid)

sales_nn %>% 
  summarytools::descr() %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')

sales_nn %>% 
  select(-c(knn, longitude,  latitude, m, subject_cluster)) %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')
```

\elandscape

### Plot nearest neighbours

```{r}
leaflet_plot(sales_nn,
             subject_lng,
             subject_lat)
```

```{r}
set_lists_to_chars <- function(x) {
  paste(unlist(x), sep='', collapse=', ')
}
test <- sales_nn

test$knn <- mapply(set_lists_to_chars, sales_nn$knn)
```


