---
title: "Clustering Example Shiny"
author: "Oliver Summers"
date: "16/11/2020"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 999)

library(bearing)
library(dplyr)
library(sf)
library(ggplot2)
library(summarytools)
library(kableExtra)
library(shiny)
library(leaflet)
library(DT)
library(mapview)
```

## Load Dataset

```{r echo=FALSE}
inputPanel(
  fileInput('data',
            label = 'Property Data',
            accept = c('.rds','.RData')
  )
)

apt <- reactive({
    readRDS(input$data$datapath) %>% 
      janitor::clean_names() %>% 
      as.data.frame()
})

renderUI({
  
  req(input$data)
  
  inputPanel(
    selectInput(
      'id',
      label = 'Select property id variable name',
      choices = colnames(apt())
    ),
    selectInput(
      'address',
      label = 'Select property address variable name',
      choices = colnames(apt())
    )
  )
})

clean_apt <- reactive({
  req(input$id)
  req(input$variables)
  
  apt() %>% 
    dplyr::rename(pid = input$id,
                  address = input$address)
})

```


## Choose the variables to use in the clustering algorithm:
```{r echo=FALSE}
renderUI({
  req(input$data)
  
  inputPanel(
    selectInput('variables',
                label= "Clustering Variables",
                choices = colnames(apt()),
                multiple = TRUE
    )
  )
})
```

## Select if variables are numeric or categorical
```{r echo=FALSE}
renderUI({
  req(input$variables)
  
  inputPanel(
  conditionalPanel(
    condition = "input['variables'].length > 0",
    checkboxGroupInput("numeric_variables",
                      label = "Numeric Variables",
                      choices = input$variables,
                      # multiple = TRUE
                      )
  ),
  conditionalPanel(
    condition = "input['variables'].length > 0",
    checkboxGroupInput("categorical_variables",
                      label = "Categorical Variables",
                      choices = input$variables,
                      # multiple = TRUE
                      )
  )
)
})
```

## Variable weights
```{r echo=FALSE}
renderUI({
  req(input$variables)
  
  inputPanel(
  conditionalPanel(
    condition = "input['variables'].length > 0",
    sliderInput("num_weights",
                 "How many variables will have a weight greater than 1?",
                 value = 0,
                 min = 0,
                 # max = length(input$variables),
                max= 3,
                 step = 1),
  ), 
  conditionalPanel(
    condition = "input['num_weights'] > 0",
    selectInput('weight_1_name',
                label = 'Weight 1',
                choices = input$variables),
    sliderInput('weight_1',
                'Weight 1 Value:',
                value = 1,
                min = 1, 
                max = 10)
  ),
  conditionalPanel(
    condition = "input['num_weights'] > 1",
    selectInput('weight_2_name',
                label = 'Weight 2',
                choices = input$variables),
    sliderInput('weight_2',
                'Weight 2 Value:',
                value = 1,
                min = 1, 
                max = 10)
  ),
  conditionalPanel(
    condition = "input['num_weights'] > 2",
    selectInput('weight_3_name',
                label = 'Weight 3',
                choices = input$variables),
    sliderInput('weight_3',
                'Weight 3 Value:',
                value = 1,
                min = 1, 
                max = 10)
  )
)
})


var_weights <- reactive({
  req(input$num_weights)
  
  if(input$num_weights == 0){
    var_weights <- NULL
  }
   if(input$num_weights == 1){
    var_weights <- c(input$weight_1)
    names(var_weights) <- c(input$weight_1_name)
   }

 if(input$num_weights == 2){
    var_weights <- c(input$weight_1, input$weight_2)
    names(var_weights) <- c(input$weight_1_name, input$weight_2_name)
 }
 if(input$num_weights == 3){
  var_weights <- c(input$weight_1, input$weight_2, input$weight_3)
    names(var_weights) <- c(input$weight_1_name, input$weight_2_name, input$weight_3_name)
 }
  var_weights

})
```

## Select the Subject Property
```{r include=FALSE}
non_na <- reactive({
  req(input$variables)
  
  clean_apt() %>% 
    select(c(input$variables, 'pid', 'latitude','longitude','address')) %>%
    na.omit() 
})

```


```{r echo=FALSE}
renderUI({
  inputPanel(
    selectInput('pid', label= "Property ID", choices = non_na() %>% select(pid) %>% unique())
    )
})
```


```{r include=FALSE}
subject <- reactive({
  req(input$pid)
  
  subj_data <- non_na() %>%
    dplyr::filter(pid == input$pid)
  
  list(subject_lat = subj_data$latitude, 
       subject_lng = subj_data$longitude, 
       subject_pid = subj_data$pid,
       subject_address = subj_data$address)
})
```

## Initial Leaflet Plot - Dataset A

This plot includes all of the properties in the dataset.

```{r echo=FALSE}
renderLeaflet({
  bearing::leaflet_plot(non_na(), subject_lat = subject()$subject_lat, subject_lng = subject()$subject_lng)
})

downloadHandler(
    filename =  'all_properties_leaflet.png',
    # content is a function with argument file. content writes the plot to the device
    content = function(file) {
      mapshot(bearing::leaflet_plot(non_na(), 
                           subject_lat = subject()$subject_lat, 
                           subject_lng = subject()$subject_lng)
               , file = file
               , cliprect = "viewport" # the clipping rectangle matches the height & width from the viewing port
               , selfcontained = FALSE)
    
    } 
)

```

## Clustered properties - Dataset B
```{r echo=FALSE}
inputPanel(
  actionButton('run_cluster',
               'Re-run clustering algorithm',
               icon = icon('refresh')
  )
)
```


```{r include=FALSE}
clustered <- reactive({
  input$run_cluster
  
  isolate({
    apt <- non_na() %>%
      mutate(across(input$numeric_variables, as.numeric),
            across(input$categorical_variables, as.factor)) %>%
      reproject_latlon()
      
    set.seed(100)
  
    m <- optimal_m(apt %>% select(-c(lon,lat,pid,address)),
                   m_values = 4:10,
                   n_start = 1)
    
    clusters <- cknn(
        data = apt %>% select(-c(lon,lat,pid,address)),
        lon = apt %>% pull(lon),
        lat = apt %>% pull(lat),
        m = m,
        k = input$k,
        l = input$l,
        var_weights = var_weights()
      )
  
    sales_with_knn <- recombine_data_knn(apt, clusters)
    
    # reproject lat/lon to GPS coordinates - use colorado
    sales_with_knn <- reproject_latlon(sales_with_knn, old_crs = 3502, new_crs = 4326) %>%
      rename(latitude = lat,
             longitude = lon)
    
    sales_with_knn
  })
})
```


This dataset includes the subject property and the other properties in its cluster.

```{r echo=FALSE}
renderText({
  sales_with_knn <- clustered()
  spid <-subject()$subject_pid
  subj_cluster <- get_subj_cluster(sales_with_knn, subject_pid = spid)

  paste('The subject property is in cluster ', subj_cluster)
})
```



### Summary stats of cluster

We can then explore the summary statistics of the subject properties cluster, as well as compare to other clusters via histograms and boxplots. I have chosen to analyse PriceSold, but other variables can also be examined.


```{r echo=FALSE}
renderDataTable({
  sales_with_knn <- clustered()
  
  subj_cluster <- get_subj_cluster(sales_with_knn, subject_pid = subject()$subject_pid)

  sales_with_knn %>%
    filter(m == subj_cluster) %>%
    select(-c(knn,latitude,longitude, m)) %>%
    summarytools::descr()

})

```


### Choose numeric variable:

```{r echo=FALSE}
renderUI({
  req(input$numeric_variables)
  
  inputPanel(
    radioButtons(
      inputId = 'plot_variable',
      label = 'Variable to plot',
      choices = input$numeric_variables
    )
  )
})
```

```{r echo=FALSE}
renderPlot({
  facet_boxplot(clustered(), variable = input$plot_variable)
})
```

```{r echo=FALSE}
renderPlot({
  facet_hist(clustered(), variable = input$plot_variable)
})
```

### Choose categorical variable: 
```{r echo=FALSE}
renderUI({
  req(input$categorical_variables)
  
  inputPanel(
    radioButtons(
      inputId = 'plot_cat_variable',
      label = 'Variable to plot',
      choices = input$categorical_variables
    )
  )
})
```


```{r echo=FALSE}
renderPlot({
  ggplot2::ggplot(clustered(), aes_string(x=input$plot_cat_variable)) +
    geom_bar() +
    facet_grid(m ~ .)
})
```

### Plot same cluster apartments

```{r echo=FALSE}
renderUI({
  inputPanel(
    selectInput(
      'cluster',
      label = 'Choose cluster to plot (default = subject cluster)',
      choices = clustered()$m %>% unique(),
      selected = get_subj_cluster(clustered(), subject_pid = subject()$subject_pid)
    )
  )
})
```

This plot shows the subject property and other properties that were found to be in the same cluster as it.
```{r echo=FALSE}
renderLeaflet({
  data <- clustered()
  
  bearing::leaflet_plot(data %>% dplyr::filter(m == input$cluster),
                        subject_lat = subject()$subject_lat,
                        subject_lng = subject()$subject_lng)

})

downloadHandler(
    filename =  'cluster_leaflet.png',
    # content is a function with argument file. content writes the plot to the device
    content = function(file) {
      mapshot(bearing::leaflet_plot(clustered() %>% dplyr::filter(m == input$cluster),
                        subject_lat = subject()$subject_lat,
                        subject_lng = subject()$subject_lng)
               , file = file
               , cliprect = "viewport" # the clipping rectangle matches the height & width from the viewing port
               , selfcontained = FALSE)
    
    } 
)

```

## Nearest Neighbours - Dataset C

This dataset includes the subject property and it's nearest neighbours from the knn algorithm.


### Select importance of distance and number of nearest neighbours:

Distance importance is a hyperparameter representing the trade-off between distance and characteristics in the kNN matching. A value equal to 1 will match on distance only, while value equal to 0 will disregard distance and match on characteristics only.

If selections are changed, please re-run the clustering algorithm (action button above)

```{r echo=FALSE}
inputPanel(
  sliderInput('l',
              label= "Importance of distance",
              min=0,
              max=1,
              value=0.5
  ),
  sliderInput('k',
              label = 'Number of nearest neighbours',
              min=1,
              max=15,
              value = 10,
              step=1)
)
```


### NN summary stats
```{r echo=FALSE}
renderDataTable({
  sales_nn <- get_nn(clustered(), subject_pid = subject()$subject_pid)
  
  sales_nn %>%
    select(-c(knn,latitude,longitude, m)) %>% 
    summarytools::descr()
})
```

```{r echo=FALSE}
DT::dataTableOutput('nn')

output$nn <- renderDT({
  get_nn(clustered(), subject_pid = subject()$subject_pid) %>% 
    select(-c(pid,m,latitude,longitude,knn))
})
```

#### Selected Rows (if relevant)

```{r echo=FALSE}
renderDT({
  req(input$nn_rows_selected)
  
  s <- input$nn_rows_selected
  data <- (get_nn(clustered(), subject_pid = subject()$subject_pid) %>% 
    select(-c(pid,m,latitude,longitude,knn)))
  data[s,]
})



data <- reactive({
  req(input$variables)
  
  set_lists_to_chars <- function(x) {
    paste(unlist(x), sep = '', collapse = ', ')
  }
  
  data <-
    get_nn(clustered(), subject_pid = subject()$subject_pid) %>%
    select(-c('address', 'latitude', 'longitude', input$variables)) %>%
    inner_join(clean_apt()
               , by = 'pid')
  
  data$knn <- mapply(set_lists_to_chars, data$knn)
  
  data
  
})





downloadHandler(
  filename =  function() {
      paste(subject()$subject_address, "_nn.csv", sep = "")
    },
    # content is a function with argument file. content writes the plot to the device
    content = function(file) {
      
      write.csv(data()
        ,
        file)
    
    },
    outputArgs = c(label = 'Download CSV')
)


```

### Choose numerical variable:
```{r echo=FALSE}
renderUI({
  req(input$numeric_variables)
  
  inputPanel(
    radioButtons(
      inputId = 'plot_variable_nn',
      label = 'Variable to plot',
      choices = input$numeric_variables
    )
  )
})
```

### NN analysis

```{r echo=FALSE}
renderPlot({
  sales_nn <- get_nn(clustered(), subject_pid = subject()$subject_pid)
  
  facet_hist(sales_nn, variable = input$plot_variable_nn)
})
```

```{r echo=FALSE}
renderPlot({
  sales_nn <- get_nn(clustered(), subject_pid = subject()$subject_pid)
  
  facet_boxplot(sales_nn, variable = input$plot_variable_nn)
})
```

### Choose categorical variable:
```{r echo=FALSE}
renderUI({
  req(input$categorical_variables)
  
  inputPanel(
    radioButtons(
      inputId = 'plot_cat_variable_nn',
      label = 'Variable to plot',
      choices = input$categorical_variables
    )
  )
})
```


```{r echo=FALSE}
renderPlot({
  sales_nn <- get_nn(clustered(), subject_pid = subject()$subject_pid)
  
  ggplot2::ggplot(sales_nn, aes_string(x=input$plot_cat_variable_nn)) +
    geom_bar() +
    facet_grid(m ~ .)
})
```


### Plot nearest neighbours

```{r echo=FALSE}
renderLeaflet({
  sales_nn <- get_nn(clustered(), subject_pid = subject()$subject_pid)
  
  bearing::leaflet_plot(sales_nn,
                        subject_lat = subject()$subject_lat,
                        subject_lng = subject()$subject_lng)
})

downloadHandler(
    filename =  'nn_leaflet.png',
    # content is a function with argument file. content writes the plot to the device
    content = function(file) {
      mapshot(bearing::leaflet_plot(get_nn(clustered(), subject_pid = subject()$subject_pid),
                        subject_lat = subject()$subject_lat,
                        subject_lng = subject()$subject_lng)
               , file = file
               , cliprect = "viewport" # the clipping rectangle matches the height & width from the viewing port
               , selfcontained = FALSE)
    
    } 
)
```
