---
author: "Oliver Summers"
date: 'Date of Analysis: `r Sys.Date()`'
output:
  pdf_document: default
  html_document: default
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
options(scipen = 999)

# required packages
library(bearing)
library(dplyr)
library(sf)
library(ggplot2)
library(summarytools)
library(kableExtra)

# ggplot theme - can make bearing one in the future
theme_set(theme_minimal())

#import data
data("ApartmentDataR")
Apartments2 <- dplyr::left_join(Apartments, AssessorInfo, by = c("APN" = "APN"))
Apartments2 <- Apartments2[!duplicated(Apartments2),] %>% 
    # can remove this after standardise columns is used. 
  janitor::clean_names() %>% 
  rename(pid = apn)

# standardise columnnames 
# standardised_data <- standarise_colnames(data,
#                                          data_src = '',
#                                          data('data_mapping'))

# Define the subject property
p_id <- Apartments2$pid[1] # get rid of this when using it in a loop

define_subject(Apartments2,
               subject_pid = p_id)
```

---
title: "Market Analysis: `r subject_address`"
---
\newpage

## Initial Leaflet Plot - Dataset A


```{r}
leaflet_plot(Apartments2, 
             subject_lng, 
             subject_lat)
```

This plot includes all of the properties in the dataset. 

```{r}

## Data Preparation
# We need to select columns to feed in to the clustering algorithm, using a select statement. 
# Unfortunately, the algorithm cannot handle missing values (NA), so we need to omit these rows. 
# In the future, we could look to impute these values. All values need to be converted to either numeric 
# (for k-means) or factor (for k-modes). Finally, the lat/lon values (in GPS coords) need to be reprojected
# into a planar projection for the knn algorithm.

prop_data <- Apartments2 %>%
  no_br() %>% 
  price_per() %>% 
  mutate(year_sold = lubridate::year(date_sold)) %>%
  select(pid,
         address,
         date_sold,
         down_payment,
         studio,
         sq_ft,
         yr_blt,
         land_sf,
         no_units,
         ppunit,
         ppsf,
         no_br,
         price_sold,
         zip,
         year_sold,
         longitude,
         latitude) %>%
  na.omit() %>%
  filter(yr_blt != 0) %>%
  mutate(across(c(down_payment:price_sold), as.numeric),
         across(c(zip:year_sold), as.factor)) %>% 
  reproject_latlon() %>% 
  as.data.frame()
```

\newpage
\blandscape
## Grouped Properties (Clusters) - Dataset B

```{r}
set.seed(100)

m <- optimal_m(prop_data %>% select(-c(lon,lat,pid,address,date_sold)),
               m_values = 4:10,
               n_start = 1)

k <- 10

clusters <- cknn(
    data = prop_data %>% select(-c(lon,lat,pid,address,date_sold)),
    lon = prop_data %>% pull(lon),
    lat = prop_data %>% pull(lat),
    m = m,
    k = k,
    l = 0.5
  )

sales_with_knn <- recombine_data_knn(prop_data, clusters)

# reproject lat/lon to GPS coordinates - use colorado
sales_with_knn <- reproject_latlon(sales_with_knn, old_crs = 3502, new_crs = 4326) %>%
  rename(latitude = lat,
         longitude = lon) %>% 
  mutate(m = as.factor(m))
```

`r subject_address` is in cluster `r get_subj_cluster(sales_with_knn, subject_pid)` of `r m`.

### Summary stats of cluster

```{r}
subj_cluster <- get_subj_cluster(sales_with_knn, subject_pid)

sales_with_knn <- sales_with_knn %>% 
  mutate(subject_cluster = ifelse(m == subj_cluster, 'yes', 'no'))

sales_with_knn %>% 
  # mutate(across(where(is.numeric), format, digits=4,nsmall = 0)) %>% 
  filter(m == subj_cluster) %>%
  summarytools::descr() %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')


# sales_with_knn %>% 
#   select(-c(knn, longitude,  latitude, m)) %>% 
#   kbl %>% 
#   kable_paper("hover", full_width = F) %>% 
#   kable_styling(latex_options='scale_down')
```
\elandscape

```{r}
facet_boxplot(sales_with_knn, variable = 'price_sold')
```

```{r}
facet_hist(sales_with_knn, 'price_sold')
```

```{r}
sales_time_scatter(sales_with_knn)
```

```{r}
ggplot2::ggplot(sales_with_knn, ggplot2::aes(x = price_sold, fill = subject_cluster)) +
  ggplot2::geom_histogram(data=subset(sales_with_knn,subject_cluster == 'no'), alpha = 0.6) +
  ggplot2::geom_histogram(data=subset(sales_with_knn,subject_cluster == 'yes'), alpha = 0.6) +
  scale_fill_manual(name="Subject Cluster", values=c("darkgreen","lightblue"),labels=c("no","yes"))
```
\newpage

### Within Cluster Analysis

```{r}
ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = price_sold)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = as.numeric(as.character(year_sold)))) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  xlab('Year Sold')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = sq_ft)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             aes(y = 0),
             color = 'red',
             size = 2) +
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = price_sold, y = no_br, group = no_br)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2)

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = sq_ft, y = no_br, group = no_br)) +
  geom_boxplot() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2)

sales_time_scatter(sales_with_knn %>% 
                     filter(m == subj_cluster))

sales_time_scatter(sales_with_knn %>% 
                     filter(m == subj_cluster),
                   sales_var = 'ppsf')

ggplot(sales_with_knn %>% 
         filter(m == subj_cluster),
       aes(x = sq_ft, y = price_sold)) +
  geom_point() +
  geom_point(data = sales_with_knn %>% 
               filter(pid == subject_pid),
             color = 'red',
             size = 2) +
  geom_smooth(method='lm', formula= y~x)
```


### Plot same cluster apartments

This plot shows `r subject_address` and the properties that were found to be in the same cluster as it.
```{r}
plot_clusters(sales_with_knn)
```

\newpage
\blandscape

## Nearest Neighbours - Dataset C

This dataset includes `r subject_address` and it's `r k` nearest neighbours from the knn algorithm.

### NN summary stats


```{r}
sales_nn <- get_nn(sales_with_knn, subject_pid)

sales_nn %>% 
  summarytools::descr() %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')

sales_nn %>% 
  select(-c(knn, longitude,  latitude, m, subject_cluster)) %>% 
  kbl(digits = 2) %>% 
  kable_paper("hover", full_width = F) %>% 
  kable_styling(latex_options='scale_down')
```

\elandscape

### Plot nearest neighbours

```{r}
leaflet_plot(sales_nn,
             subject_lng,
             subject_lat)
```

```{r}
set_lists_to_chars <- function(x) {
  paste(unlist(x), sep='', collapse=', ')
}
test <- sales_nn

test$knn <- mapply(set_lists_to_chars, sales_nn$knn)
```


